---
title: "CPD Report"
author: "Jack Kennedy"
output:
  html_document:
  theme: united
toc: true
toc_float: true
number_sections: yes
echo: FALSE
warning: FALSE
message: FALSE
---

```{r}
#| label: r-setup
#| echo: FALSE
library("levelup")
library("lubridate")
library("gt")
library("emo")
library("dplyr")

df <- import_cpd(path = "cpd-records")
```

# Overall summary

This document contains a record of my Continuous Professional Development activities.

CPD should be a key part of a professional statistician's work ethic. CPD means the development of the "whole person" statistical and non-statistical, technical and personal. CPD evaluation is essentially a self-assessment process.

Each year, I should have at least 60 hours of learning hours, across at least three of the following pre-defined categories.

* Work based learning
* Professional activity
* Formal / educational
* Self-directed learning
* Other


```{r}
#| label: annual-total
#| echo: false
df <- df %>%
  mutate(year = year(start_date)) %>%
  mutate(learning_hours = as.numeric(learning_hours))

df %>%
  group_by(year) %>%
  summarise(total_hours = sum(learning_hours)) %>%
  mutate(emoji = ifelse(total_hours >= 60, emo::ji("check"), emo::ji("x"))) %>%
  arrange(desc(year)) %>%
  gt() %>%
  cols_label(
    year = md("**Year**"),
    total_hours = md("**Learning Hours**"),
    emoji = ""
  )
```

```{r, echo = FALSE, results = "asis"}
#| results: "asis"
years <- sort(unique(df$year), decreasing = TRUE)

md <- lapply(years, function(y) {
  knitr::knit_child(
    'annual-template.qmd', envir = environment(), quiet = TRUE
  )
})

cat(unlist(md), sep = '\n')
```
